Compare pseqs

### 2019-05-29 comparepseqs.Rmd
ggpairs

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(parallel)
library(knitr)
library(gridExtra)
library(vegan)
library(ggpubr)
library(broom)
library(tidyr)
```

@@

@@

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]])
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = scale(diversities_shannon))

@@

    ret[[key]] = list("alphadiversity" = alphadiversity,
                      "betadiversity" = betadiversity)
}
```

@@

```{r debug alpha, eval = FALSE}
alphadiversity <- readRDS(file = paste0("rds-comparepseqs/alpha-R16S.rds"))
alphadiversity

>>>>

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(parallel)
library(knitr)
library(gridExtra)
library(vegan)
library(ggpubr)
library(broom)
library(tidyr)
library(GGally)
```

@@

    if (!file.exists(paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))) {
        missing$alphadistribution = TRUE
    } else {
        alphadiversity <- readRDS(file = paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))
    }

@@

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]])
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = as.numeric(scale(diversities_shannon)))

        if ("alphadistribution" %in% names(missing)) {
            message("Missing alpha distribution")
            alphadistribution <- dset %>%
                mutate(!!key := diversities_shannon) %>%
                select(Sample_ID, key)
            saveRDS(alphadistribution, file = paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))
        }

@@

    ret[[key]] = list("alphadiversity" = alphadiversity,
                      "betadiversity" = betadiversity,
                      "alphadistribution" = alphadistribution)
}
```

@@

```{r debug alpha, eval = FALSE}
scatterplot.df <- lapply(ret, function(x) x$alphadistribution) %>%
    Reduce(function(x, y) merge(x, y, all=TRUE, by="Sample_ID"), .) %>%
    select(-Sample_ID) %>%
    na.omit()

ggsave(file = paste0("cache/ggpairs-alphas.png"),
       plot=ggpairs(scatterplot.df,
                        lower = list(continuous = wrap("points",
                                                       alpha = 0.3,
                                                       size=0.1), 
                                     combo = wrap("dot",
                                                  alpha = 0.4,
                                                  size=0.2))),
       height=6,
       width=9,
       unit = "in",
       dpi = 300)
